---
title: "LB_ShinyAPP"
author: "Laurent Brodier"
date: "18/06/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
### Description
- The app enables to do clustering on multiple datasets.
- The ouput displays a scatterplot or a dendrogram. 
<br><br>
  
### Where to find the app?
- The app is located <a href="https://lbrodier87.shinyapps.io/lb_shinyapp/">here</a>
- The documentation can be found <a href="https://lbrodier87.github.io/DataProductsWeek4LB/Documentation_LB_ShinyApp.html">here </a>

## How to use the App: 
  
- Select the **dataset**
- Select the **X Variable**  and **Y Variable**
- Select the **Clusering method** (k-means or hclust)
- Select the target **number of clusters**
  
  <br>
*The output is displayed on the right:*
  
- A scatter plot for k-means  
- A dendrogram for hclust
  
## k-means
```{r}
library(ggplot2)
df <- iris[,c(1,3)]
df <- na.omit(df)
k <-  kmeans(df, 3)
cluster <- as.factor(k$cluster)
centers <- as.data.frame(k$centers)
centers$color= as.factor(1:nrow(centers))
ggplot(data=df, aes(x=df[,1], y=df[,2])) + 
                geom_point(aes(color=cluster), alpha=0.5, size=2) + 
                geom_point(data=centers, inherit.aes = F, aes(x=centers[,1], y=centers[,2], color=color), 
                           shape=3, size=5) + 
                theme_bw() + labs(x=names(iris)[1], y=names(iris)[3], title = "k-mean clustering") 
```
  
This is an example of k-means clustering on dataset *iris* with *k-means* and *6 clusters*. 

## hierarchical clustering: 
```{r}
df <- mtcars
            d <- dist(df, method = "euclidean") # distance matrix
            fit <- hclust(d, method="ward.D2")
            plot(fit, xlab ="observation") # display dendogram
            groups <- as.factor(cutree(fit, k=3)) # cut tree into 5 clusters
            rect.hclust(fit, k=3, border="red")
```
  
This is an example of *hclust* on the dataset *mtcars* with *3 clusters*. 
